Transformer-Based Reranking for Improving Korean Morphological Analysis System

### 2023-12-29 contents/draft.tex

\begin{document}
    \title{Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking}

@@

    \abstract[Abstract]{
        This study introduces a new approach in Korean morphological analysis, combining dictionary-based techniques with Transformer-based deep learning models.
        A key innovation is the use of a BERT-based re-ranking system, significantly enhancing the accuracy of traditional morphological analysis.
        The methodology generates multiple suboptimal paths, then employs BERT models for re-ranking, leveraging their advanced language comprehension.

        Results show remarkable performance improvements, with the first-stage re-ranking achieving over 20\% improvement in Error Reduction Rate (ERR) compared to existing models.
        The second-stage, utilizing a different BERT variant, further increases this improvement in ERR to over 30\%.
        This indicates a significant leap in accuracy, validating the effectiveness of merging dictionary-based analysis with contemporary deep learning.

        The study suggests future exploration in refined integrations of dictionary and deep learning methods and using probabilistic models for enhanced morphological analysis.
        This hybrid approach sets a new benchmark in the field and offers insights for similar challenges in language processing applications.
    }
    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, re-ranking}

@@

    Several approaches have been suggested for morphological analysis, a critical aspect of Korean language comprehension~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
    Typically, when individuals grasp spoken or written language, they try to comprehend it through familiar vocabulary and concepts.
    While some approaches rely on rules or dictionaries to capture this understanding~\cite{KwonHC1991}, constructing and updating dictionaries for varied text vocabularies can be challenging.
    As a result, methods focusing on tagging syllable units without a dictionary have been proposed~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016} and studied for enhancement~\cite{KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
    Mechanically, syllable-by-syllable morphological analysis can be achieved by either tagging syllables and then applying a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or by tagging syllables with the base form pre-restored~\cite{YounJY2021}.
    However, this approach has limitations, struggling with precise morpheme boundary identification and struggling to grasp long-term contextual information as the sequence lengthens.
    In this study, the former is termed dictionary-based morphological analysis, and the latter is syllable-unit morphological analysis.
    Both methods are trained on manually labeled corpora, facing challenges in accurately analyzing new syllable combinations or morphemes absent in the training data.
    The evolution of the Internet, open sources, and shared knowledge has led to substantial accumulations of web texts, corpora, language resources, offering an opportunity to overcome the constraints of dictionary-based methods due to reduced costs in dictionary construction and maintenance.

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;block-v1}}
        \caption{Overall process flow of the proposed method}
        \label{fig:block}
    \end{figure*}

    To pinpoint instances where a suboptimal solution may, in fact, be the best choice according to the best path calculation, we modified the best path calculation method to yield suboptimal analysis results and assessed their accuracy.
    While various approaches exist for selecting the next-best path, we opted for the method of substituting a morpheme node on the optimal path with a lower-ranked node.
    Table~\ref{tab:maximum-performance} illustrates the degree to which analysis performance can be enhanced by replacing the optimal path with a lower-ranked node.
    This problem is analogous to the challenge of re-ranking search results in information retrieval~\cite{BaeYJ2021}, where the goal is to identify the correct answer among the generated suboptimal results.

    In ~\cite{ChoiYS2018}, the N-best analysis results produced by the seq2seq model were re-ranked based on a convolutional neural network to enhance performance.
    In our study, we employed re-ranking with two distinct BERT models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
    Experimental results reveal that first-stage re-ranking improves performance by over 20\% compared to existing written and spoken models.
    Furthermore, second-stage re-ranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared to existing written and spoken models.

    While our introduced method led to further enhancement in the performance of the dictionary-based morphological analysis, it resulted in an overall increase in analysis time when configuring the morphological analysis system, including the re-ranking model itself.
    However, a promising avenue for future exploration lies in utilizing the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in a dictionary, akin to the backpropagation process in a typical neural network.
    It is anticipated that an improved morphological analysis system with updated connection costs can generate superior re-ranking candidates, potentially enabling iterative performance improvements.
    While this study focused on two-stage re-ranking, further research is essential to fully explore this potential.

@@

    The primary contributions of this study can be summarized as follows:
    \begin{enumerate}
        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We investigate the potential for performance improvement by introducing a method to replace the optimal path with a suboptimal node. Additionally, we propose an effective approach to enhance the dictionary-based morphological analysis method through deep learning.
        \item \textbf{Extending the performance improvement by introducing a two-stage re-ranking model}: To further enhance the performance of dictionary-based analysis through re-ranking, we suggest extending the improvement using different BERT models and conducting two rounds of re-ranking.
        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We present a novel method for updating dictionary connection costs based on re-ranked morphological analysis results. Furthermore, we outline directions for future research, suggesting potential enhancements.
    \end{enumerate}
    These contributions provide valuable insights into advancing the performance of Korean morphological analysis and offer guidance for future researchers.

    The subsequent sections of this paper are organized as follows:
    Section ~\ref{sec:morphological-analysis-model} discusses the configuration and training of a dictionary-based morphological analysis system.
    Section ~\ref{sec:reranking-model} covers the generation of secondary results of morphological analysis, the production of re-ranking data, and the proposal of a method for training a two-stage re-ranking model.
    Section ~\ref{sec:results} delves into the results of the performance improvement using morphological analysis and re-ranking models.
    Section ~\ref{sec:related-work} introduces previous research cases related to this study.
    Finally, in Section ~\ref{sec:conclusion}, we conclude the study, discuss its limitations, and suggest directions for future research.

@@

    Our proposed method for enhancing Korean morphological analysis involves integrating a Transformer-based re-ranking model into a dictionary-based morphological analysis system.
    Our approach is depicted in Figure~\ref{fig:block}, which illustrates the overall process flow.
    This section details the configuration and training of a dictionary-based morphological analysis system.

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
        \caption{Example of lattice construction and decoding result and secondary path generation}
        \label{fig:lattice}
    \end{figure*}

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
        \caption{Two-stage re-ranking model for Korean morphological analysis}
        \label{fig:ranking}
    \end{figure*}

    \section{Re-ranking Model}\label{sec:reranking-model}

    While dictionary-based morphological analysis provides substantial advancements, it is not immune to instances where its optimal paths deviate from the correct solutions perceived by humans.
    To address this, we introduce a re-ranking model that revisits these initial results and adjusts them to enhance accuracy.
    This re-ranking approach involves generating multiple analyses of an input and subsequently rearranging them using a new set of criteria or models.
    Here, the BERT-based models play a pivotal role.

@@

    Before the re-ranking process initiates, multiple analyses, commonly referred to as N-best paths, of the input sentence are generated.
    This involves extracting the top N candidates from the lattice structure.
    In our study, a novel approach is introduced to produce secondary paths, as depicted in (3) of Figure~\ref{fig:lattice}, by selecting the second-best node instead of each best node constituting the path from the best-path result.
    Some of these secondary paths offered alternatives that reconciled incorrect answers with correct ones.
    Similarly, paths modified by favoring the third-best node were termed tertiary paths, and this nomenclature continued for subsequent paths.
    In our preliminary test, the secondary paths, encompassing both optimal and suboptimal paths, demonstrated coverage of the majority of correct morphological analyses, as assessed through human evaluations (refer to Table~\ref{tab:maximum-performance}).

    \subsection{BERT-based Re-ranking}\label{subsec:bert-based-reranking}

@@

    Once the BERT model is fine-tuned and trained for the re-ranking task, it can predict a re-ranking score for each path in the secondary path list.
    This means that, taking into account the context, morphological organization, and other crucial linguistic features of the path, the model assigns a score to each path.
    Subsequently, the paths are re-ranked based on these scores, and the path with the highest score is selected as the optimal morphological analysis.

    \subsection{Two-stage Re-ranking}\label{subsec:two-stage-reranking}

    Given the complexity of the Korean language, a single re-ranking step does not constantly yield accurate results.
    Therefore, we propose a two-step re-ranking approach as described in ~\cite{Nogueira2019}.

    In the first step, we re-rank the secondary paths generated using the BERT model, as outlined in Section~\ref{subsec:bert-based-reranking}.
    Subsequently, in the second step, we introduce another BERT variant optimized for a different set of linguistic features or trained on a distinct dataset.
    This enables a fine-grained re-evaluation, further refining the list and elevating more contextually accurate paths to the top.

    As shown in Figure~\ref{fig:ranking}, for a two-stage re-ranking model, the first stage conducts the initial re-ranking, taking a secondary path in morphologically tagged lemma form as input.
    The second re-ranking is then performed, taking the path re-ranked in stage 1 and the original input sentence as input.
    This approach enhances effectiveness, considering the varied input types.

    In summary, the two-stage re-ranking model depicted within Figure~\ref{fig:block} represents a significant advance in the approach to Korean morphological analysis.
    This model ingeniously integrates with the dictionary-based morphological analysis, where it employs a two-stage BERT-based re-ranking process to refine the analysis results.
    In the first stage, one BERT model is utilized to assess and re-rank the morphological paths generated by the dictionary-based analysis.
    The second stage introduces a different BERT variant, further enhancing the re-ranking accuracy by considering a diverse set of linguistic features.
    This layered approach, employing dual BERT models, is specifically designed to capture the intricacies and contextual nuances of the Korean language, addressing the challenges posed by its complex morphological structures.

    The deep learning component, particularly the BERT models, plays a pivotal role in identifying and correcting potential inaccuracies in the initial morphological analysis.
    By evaluating morphological structures and their contextual alignment, these models significantly contribute to the accuracy of our system, especially in complex linguistic scenarios that require a deeper understanding of language context.
    The experimental setup and results, detailed in the following section, provide crucial empirical evidence for the effectiveness of the re-ranking model.
    These results not only demonstrate the enhanced accuracy achieved through our innovative use of BERT models but also underscore the practical applicability of our approach in real-world Korean language processing tasks.

@@

    Having formulated the re-ranking model as a theoretical framework to enhance Korean morphological analysis, our focus now shifts to empirical validation.
    This section delineates our carefully designed experimental setup, crafted to rigorously assess the performance of our model.
    Through these experiments, our goal is not only to showcase the model's accuracy but also to highlight its practical applicability in navigating the intricacies of Korean language processing.

    Our evaluation centers on the performance of the proposed deep learning-integrated dictionary-based morphological analysis method.
    The ensuing section unfolds the results of our experimental assessment, delving into the enhancements over conventional methods and elucidating the effectiveness of our re-ranking model.

@@

    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the re-ranking model, we employed eojeol accuracy and morpheme F1 score as evaluation metrics.

@@

    \begin{table*}[ht]
        \caption{Performance comparison between morphological analysis systems without re-ranking}
        \label{tab:performance-without-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UCorpus (written)}                     & \multicolumn{2}{c}{Everyone's Corpus (written)}           \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 89.17                      & 93.06                        & 87.88                      & 92.32                        & 87.77                      & 92.05                        \\
            \hspace{2mm}Syllable-based (written)   & 91.95                      & 95.16                        & \textbf{96.84}             & \textbf{97.97}               & \textbf{98.00}             & \textbf{98.82}               \\
            \hspace{2mm}Dictionary-based (written) & 90.99                      & 94.58                        & 96.33                      & 97.74                        & 96.85                      & 98.14                        \\
            \hspace{2mm}Dictionary-based (Sejong)  & \textbf{95.23}             & \textbf{97.08}               & 90.18                      & 94.19                        & 91.30                      & 94.79                        \\
            \toprule
            \multirow{2}{*}{System}                & \multicolumn{2}{c}{UCorpus (semi-spoken)}                 & \multicolumn{2}{c}{UCorpus (spoken)}                      & \multicolumn{2}{c}{Everyone's Corpus (spoken)}            \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 86.85                      & 91.38                        & 81.75                      & 87.90                        & 85.28                      & 89.52                        \\
            \hspace{2mm}Syllable-based (spoken)    & \textbf{96.56}             & \textbf{97.65}               & \textbf{94.89}             & \textbf{96.76}               & \textbf{95.14}             & \textbf{96.82}               \\
            \hspace{2mm}Dictionary-based (spoken)  & 94.98                      & 96.65                        & 93.02                      & 95.71                        & 92.47                      & 94.83                        \\
            \bottomrule
        \end{tabular*}
    \end{table*}

>>>>

\begin{document}
    \title{Transformer-Based Reranking for Improving Korean Morphological Analysis System}

@@

    \abstract[Abstract]{
        This study introduces a new approach in Korean morphological analysis, combining dictionary-based techniques with Transformer-based deep learning models.
        The key innovation is the use of a BERT-based Reranking system, significantly enhancing the accuracy of traditional morphological analysis.
        The methodology generates multiple suboptimal paths, then employs BERT models for reranking, leveraging their advanced language comprehension.

        Results show remarkable performance improvements, with the first-stage reranking achieving over 20\% improvement in Error Reduction Rate (ERR) compared to existing models.
        The second-stage, utilizing a different BERT variant, further increases this improvement in ERR to over 30\%.
        This indicates a significant leap in accuracy, validating the effectiveness of merging dictionary-based analysis with contemporary deep learning.

        The study suggests future exploration in refined integrations of dictionary and deep learning methods and using probabilistic models for enhanced morphological analysis.
        This hybrid approach sets a new benchmark in the field and offers insights for similar challenges in language processing applications.
    }
    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, reranking}

@@

    Several approaches have been suggested for morphological analysis, a critical aspect of Korean language comprehension~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
    Typically, when individuals grasp spoken or written language, they try to comprehend it through familiar vocabulary and concepts.
    While some approaches rely on rules or dictionaries to capture this understanding~\cite{KwonHC1991}, constructing and updating dictionaries for varied text vocabularies can be challenging.
    As a result, methods focusing on tagging syllable units without a dictionary have been proposed~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016} and studied for enhancement~\cite{KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
    Mechanically, syllable-by-syllable morphological analysis can be achieved by either tagging syllables and then applying a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or by tagging syllables with the base form pre-restored~\cite{YounJY2021}.
    %However, this approach has limitations, struggling with precise morpheme boundary identification and struggling to grasp long-term contextual information as the sequence lengthens.
        However, this approach has limitations, struggling with identifying precise morpheme boundary identification and grasping long-term contextual information as the sequence lengthens.
    In this study, the former is termed dictionary-based morphological analysis, and the latter is syllable-unit morphological analysis.
    Both methods are trained on manually labeled corpora, facing challenges in accurately analyzing new syllable combinations or morphemes absent in the training data.
    The evolution of the Internet, open sources, and shared knowledge has led to substantial accumulations of web texts, corpora, language resources, offering an opportunity to overcome the constraints of dictionary-based methods due to reduced costs in dictionary construction and maintenance.

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;block-v1}}
        \caption{Overall process flow of the proposed method. Given morpheme-tagged corpus which consists of pairs of sentences and their morpheme-annotated results (in Section \ref{subsec:korean-morphological-analysis-corpora} ), the corpus preprocessing transforms a morpheme-tagged sentence into a training instance by performing the string alignment between its surface and lemma forms (in Section \ref{subsec:training-example-transformation}). Under the transformed training corpus, the dictionary-based morphological analysis model is trained using the CRF algorithm, thereby constructing morpheme-based lexicon and obtaining lexicon node values and the connection cost matrix which are used to score a morphologinal analysis path (in Section \ref{subsec:training-example-transformation}). Restricting possible paths by the morpheme-based lexicon, we construct a lattice, which compactly represents all possible paths based on a graph of nodes, where a connected path including the starting and ending nodes is considered as a morphological analysis path (in Section \ref{subsec:lattice-construction-and-decoding}). For reranking, we generate secondary paths by alternatively replacing the top nodes in the optimal path by the next-top nodes (i.e. the secondary nodes) (in Section \ref{subsec:secondary-path-generation} ). Once a set of secondary paths is produced, we further apply two-stage reranking methods that 1) first performs the BERT-based reranking over a set of secondary paths (in Section \ref{subsec:bert-based-reranking}) and then 2) carries out the additional reranking module applied on the concatenated input of a reranked path and an original input sentence (in Section \ref{subsec:two-stage-reranking}).  
        }
        \label{fig:block}
    \end{figure*}

    To pinpoint instances where a suboptimal solution may, in fact, be the best choice according to the best path calculation, we modified the best path calculation method to yield suboptimal analysis results and assessed their accuracy.
    While various approaches exist for selecting the next-best path, we opted for the method of substituting a morpheme node on the optimal path with a lower-ranked node.
    Table~\ref{tab:maximum-performance} illustrates the degree to which analysis performance can be enhanced by replacing the optimal path with a lower-ranked node.
    This problem is analogous to the challenge of reranking search results in information retrieval~\cite{BaeYJ2021}, where the goal is to identify the correct answer among the generated suboptimal results.

    In ~\cite{ChoiYS2018}, the N-best analysis results produced by the seq2seq model were reranked based on a convolutional neural network to enhance performance.
    In our study, we employed reranking with two distinct BERT models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
    Experimental results reveal that first-stage reranking improves performance by over 20\% compared to existing written and spoken models.
    Furthermore, second-stage reranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared to existing written and spoken models.

    While our introduced method led to further enhancement in the performance of the dictionary-based morphological analysis, it resulted in an overall increase in analysis time when configuring the morphological analysis system, including the reranking model itself.
    However, a promising avenue for future exploration lies in utilizing the results of multiple reranked morpheme analyses to update the connection costs between morphemes in a dictionary, akin to the backpropagation process in a typical neural network.
    It is anticipated that an improved morphological analysis system with updated connection costs can generate superior reranking candidates, potentially enabling iterative performance improvements.
    While this study focused on two-stage reranking, further research is essential to fully explore this potential.

@@

    The primary contributions of this study can be summarized as follows:
    \begin{enumerate}
        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We investigate the potential for performance improvement by introducing a method to replace some nodes in the optimal path with suboptimal ones. Additionally, we propose an effective approach to enhance the dictionary-based morphological analysis method through deep learning.
        \item \textbf{Extending the performance improvement by introducing a two-stage reranking model}: To further enhance the performance of dictionary-based analysis through reranking, we suggest extending the improvement using different BERT models and conducting two rounds of reranking.
        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We present a novel method for updating dictionary connection costs based on reranked morphological analysis results. Furthermore, we outline directions for future research, suggesting potential enhancements.
    \end{enumerate}
    These contributions provide valuable insights into advancing the performance of Korean morphological analysis and offer guidance for future researchers.

    The subsequent sections of this paper are organized as follows:
    Section ~\ref{sec:morphological-analysis-model} discusses the configuration and training of a dictionary-based morphological analysis system.
    Section ~\ref{sec:reranking-model} covers the generation of secondary results of morphological analysis, the production of reranking data, and the proposal of a method for training a two-stage reranking model.
    Section ~\ref{sec:results} delves into the results of the performance improvement using morphological analysis and reranking models.
    Section ~\ref{sec:related-work} introduces previous research cases related to this study.
    Finally, in Section ~\ref{sec:conclusion}, we conclude the study, discuss its limitations, and suggest directions for future research.

@@

    Our proposed method for enhancing Korean morphological analysis involves integrating a Transformer-based reranking model into a dictionary-based morphological analysis system.
    Our approach is depicted in Figure~\ref{fig:block}, which illustrates the overall process flow.
    This section details the configuration and training of a dictionary-based morphological analysis system.

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
        \caption{An illustrated example of a constructed lattice, the best-decoded result, and a set of the generated secondary paths. A lattice is constructed by restricting a set of nodes by morpheme lexicon, where each node is marked by its ``rank'' among a set of morphemes whose staring position are the same each other. The best path indicates the sequence of top-1 nodes in the lattice, i.e., nodes marked by the 1st rank. A secondary path is generated by replacing a top-1 node with the next top node at the same starting position, which is marked by the 2nd rank. }
        \label{fig:lattice}
    \end{figure*}

@@

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
        \caption{Two-stage reranking model for Korean morphological analysis. The \textit{BERT-based reranker} module takes a set of candidate secondary paths and predicts their projected scores on these BERT-encoded representations. The \textit{X-based reranker} module takes a concatenated input of a secondary path and an original input sentence and predicts its score based on the [CLS] token, where X is a variant of BERT models.}
        \label{fig:ranking}
    \end{figure*}

    \section{Reranking Model}\label{sec:reranking-model}

    While dictionary-based morphological analysis provides substantial advancements, it is not immune to instances where its optimal paths deviate from the correct solutions perceived by humans.
    To address this, we introduce a reranking model that revisits these initial results and adjusts them to enhance accuracy.
    This reranking approach involves generating multiple analyses of an input and subsequently rearranging them using a new set of criteria or models.
    Here, the BERT-based models play a pivotal role.

@@

    Before the reranking process initiates, multiple analyses, commonly referred to as N-best paths, of the input sentence are generated.
    This involves extracting the top N candidates from the lattice structure.
    In our study, a novel approach is introduced to produce secondary paths, as depicted in (3) of Figure~\ref{fig:lattice}, by selecting the second-best node instead of each best node constituting the path from the best-path result.
    Some of these secondary paths offered alternatives that reconciled incorrect answers with correct ones.
    Similarly, paths modified by favoring the third-best node were termed tertiary paths, and this nomenclature continued for subsequent paths.
    In our preliminary test, the secondary paths, encompassing both optimal and suboptimal paths, demonstrated coverage of the majority of correct morphological analyses, as assessed through human evaluations (refer to Table~\ref{tab:maximum-performance}).

    \subsection{BERT-based Reranking}\label{subsec:bert-based-reranking}

@@

    Once the BERT model is fine-tuned and trained for the reranking task, it can predict a reranking score for each path in the secondary path list.
    This means that, taking into account the context, morphological organization, and other crucial linguistic features of the path, the model assigns a score to each path.
    Subsequently, the paths are reranked based on these scores, and the path with the highest score is selected as the optimal morphological analysis.

    \subsection{Two-stage Reranking}\label{subsec:two-stage-reranking}

    Given the complexity of the Korean language, a single reranking step does not constantly yield accurate results.
    Therefore, we propose a two-step reranking approach as described in ~\cite{Nogueira2019}.

    In the first step, we rerank the secondary paths generated using the BERT model, as outlined in Section~\ref{subsec:bert-based-reranking}.
    Subsequently, in the second step, we introduce another BERT variant optimized for a different set of linguistic features or trained on a distinct dataset.
    This enables a fine-grained re-evaluation, further refining the list and elevating more contextually accurate paths to the top.

    As shown in Figure~\ref{fig:ranking}, for a two-stage reranking model, the first stage conducts the initial reranking, taking a secondary path in morphologically tagged lemma form as input.
    The second reranking is then performed, taking the path reranked in stage 1 and the original input sentence as input.
    This approach enhances effectiveness, considering the varied input types.

    In summary, the two-stage reranking model depicted in Figure~\ref{fig:block} represents a significant advance in the approach to Korean morphological analysis.
    This model ingeniously integrates with the dictionary-based morphological analysis, where it employs a two-stage BERT-based reranking process to refine the results of the analysis.
    In the first stage, one BERT model is utilized to assess and rerank the morphological paths generated by the dictionary-based analysis.
    The second stage introduces a different BERT variant, further enhancing the reranking accuracy by considering diverse linguistic features.
    This layered approach, employing dual BERT models, is specifically designed to capture the intricacies and contextual nuances of the Korean language, addressing the challenges posed by its complex morphological structures.

    The deep learning component, particularly the BERT models, plays a pivotal role in identifying and correcting potential inaccuracies in the initial morphological analysis.
    Moreover, by evaluating morphological structures and their contextual alignment, these models significantly contribute to the accuracy of our system, especially in complex linguistic scenarios that require a deeper understanding of language context.
    The experimental setup and results, detailed in the section 4, provide crucial empirical evidence for the effectiveness of the reranking model.
    These results not only demonstrate the enhanced accuracy achieved through our innovative use of BERT models but also underscore the practical applicability of our approach in real-world Korean language processing tasks.

@@

    Having formulated the reranking model as a theoretical framework to enhance Korean morphological analysis, our focus now shifts to empirical validation.
    This section delineates our carefully designed experimental setup, crafted to rigorously assess the performance of our model.
    Through these experiments, our goal is not only to showcase the model's accuracy but also to highlight its practical applicability in navigating the intricacies of Korean language processing.

    Our evaluation centers on the performance of the proposed deep learning-integrated dictionary-based morphological analysis method.
    The ensuing section unfolds the results of our experimental assessment, delving into the enhancements over conventional methods and elucidating the effectiveness of our reranking model.

@@

    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the reranking model, we employed eojeol accuracy and morpheme F1 score as evaluation metrics.

@@

    \begin{table*}[ht]
        \caption{Performance comparison between morphological analysis systems without reranking}
        \label{tab:performance-without-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UCorpus (written)}                     & \multicolumn{2}{c}{Everyone's Corpus (written)}           \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 89.17                      & 93.06                        & 87.88                      & 92.32                        & 87.77                      & 92.05                        \\
            \hspace{2mm}Syllable-based (written)   & 91.95                      & 95.16                        & \textbf{96.84}             & \textbf{97.97}               & \textbf{98.00}             & \textbf{98.82}               \\
            \hspace{2mm}Dictionary-based (written) & 90.99                      & 94.58                        & 96.33                      & 97.74                        & 96.85                      & 98.14                        \\
            \hspace{2mm}Dictionary-based (Sejong)  & \textbf{95.23}             & \textbf{97.08}               & 90.18                      & 94.19                        & 91.30                      & 94.79                        \\
            \toprule
            \multirow{2}{*}{System}                & \multicolumn{2}{c}{UCorpus (semi-spoken)}                 & \multicolumn{2}{c}{UCorpus (spoken)}                      & \multicolumn{2}{c}{Everyone's Corpus (spoken)}            \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 86.85                      & 91.38                        & 81.75                      & 87.90                        & 85.28                      & 89.52                        \\
            \hspace{2mm}Syllable-based (spoken)    & \textbf{96.56}             & \textbf{97.65}               & \textbf{94.89}             & \textbf{96.76}               & \textbf{95.14}             & \textbf{96.82}               \\
            \hspace{2mm}Dictionary-based (spoken)  & 94.98                      & 96.65                        & 93.02                      & 95.71                        & 92.47                      & 94.83                        \\
            \bottomrule
        \end{tabular*}
    \end{table*}

    \begin{table*}[ht]
        \caption{Performance comparison between morphological analysis systems with two-stage reranking}
        \label{tab:performance-with-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                       & \multicolumn{2}{c}{Sejong}                                             & \multicolumn{2}{c}{UC+EC (written)}                                    & \multicolumn{2}{c}{UC+EC (spoken)}                                     \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                             & \multicolumn{1}{c}{eojeol}              & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol}              & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol}              & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                          & 89.17                                   & 93.06                        & 87.83                                   & 92.19                        & 84.62                                   & 89.60                        \\
            \hspace{2mm}Syllable-based                    & 91.95                                   & 95.16                        & 97.42                                   & 98.39                        & 95.53                                   & \textbf{97.08}               \\
            \hspace{2mm}Dictionary-based (without rerank) & 95.23\footnotesize{ [+0.0\%]}           & 97.08                        & 96.59\footnotesize{ [+0.0\%]}           & 97.94                        & 93.49\footnotesize{ [+0.0\%]}           & 95.73                        \\
            \hspace{2mm}Dictionary-based (1-stage rerank) & 96.63\footnotesize{ [+29.2\%]}          & 97.84                        & 97.50\footnotesize{ [+26.7\%]}          & 98.44                        & 94.77\footnotesize{ [+19.6\%]}          & 96.62                        \\
            \hspace{2mm}Dictionary-based (2-stage rerank) & \textbf{96.87}\footnotesize{ [+34.4\%]} & \textbf{98.01}               & \textbf{97.75}\footnotesize{ [+34.1\%]} & \textbf{98.60}               & \textbf{95.56}\footnotesize{ [+31.8\%]} & \textbf{97.08}               \\
            \bottomrule
        \end{tabular*}
        \begin{tablenotes}
            \footnotesize
            \item\hspace{2mm} * The numbers in parentheses represent the Error Reduction Rate (ERR), calculated with respect to the ``Dictionary-based (without rerank)'' as the baseline.
        \end{tablenotes}
    \end{table*}
